A Systematic Approach to Model Predictive Controller Constraint Handling: Rigorous Geometric Methods

### 2010-12-14 article.tex
Don't mention user interaction
Corrected celsius

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}

\newcommand{\vect}[1] %vector notation
{{\bf {#1}}}
\newcommand{\npoly}{$n$-polytope}
\newcommand{\citepp}[4] %double parenthesis cite
{(\citealp[{#1}]{{#2}}; \citealp[{#3}]{{#4}})}
\newcommand{\degrees}[1]{^{\circ}\text{{#1}}} %degree symbol
\newcommand{\bpm}{\begin{pmatrix}} %for matrix notation
\newcommand{\epm}{\end{pmatrix}}

@@

Mathematical rigour and unambiguous language for identifying constraint types were key design criteria. 
Ample feedback to the user was added to provide a supportive rather than prescriptive environment.
The application of the method is illustrated for a laboratory scale distillation column running commercial MPC packages.
\end{abstract}

@@

Table~\ref{tab:columnopcon} lists the operating conditions of the distillation column.
\begin{table}[htbp]
  \centering
  \begin{tabular}{llllll}
    \toprule
    \multicolumn{2}{c}{Variable} & \multicolumn{4}{c}{Constraints}\\
     && \multicolumn{2}{c}{Operating} & \multicolumn{2}{c}{Physical} \\
    \cmidrule(r){3-4} \cmidrule(r){5-6}
    && Low & High & Low & High \\ 
    \midrule
    Inputs &$R~(\text{mA})$          & 11 & 15 & 4 & 20 \\
           &$T_{10~sp}~(\degrees{C})$ & 78 & 82 & 25 & 90 \\[1.3ex]
    Outputs &$T_1~(\degrees{C})$     & 66 & 68 & 15 & 68 \\
            &$T_{8}~(\degrees{C})$   & 78 & 82 & 25 & 90 \\
    \bottomrule
  \end{tabular}
  \caption{Operating conditions of the laboratory distillation column.}
  \label{tab:columnopcon}
\end{table}

@@

Figure~\ref{fig:columnaisaos}(c) focuses on the intersection of the AOS and the DOS.
The calculated OI is 0.006 which confirms that only a very small operating region within the DOS is attainable.
It is also clear that the upper limit of 82$\degrees{C}$ on $T_8$ is unrealistic as the maximum value of $T_8$ (in the desired operating region) is only 78.2$\degrees{C}$.

@@

The dark triangle in figure~\ref{fig:columnfitbox} represents the constraints defining the intersection.
An unmeasured variable needs to be added to the process model to implement the diagonal constraint ($0.88T_8-0.47T_1\leq 36.56\degrees{C}$).
Naming the new output $y_1$ and augmenting the process model matrix as shown in equation~\ref{eq:columnnewmodel} allows for the diagonal (linear) constraint to be expressed simply as {$y_1~\leq~36.56\degrees{C}$}.
\begin{equation}
  \label{eq:columnnewmodel}
  G_{new}= \bpm -0.0575 & 0.96 \\       % T1
                  -0.146  & 0.518 \\      % T8
                   0.0956 & 1.30 \\ \epm  %y1
\end{equation}

@@

\section{Conclusions}\label{sec:conclusions}
Form the proposed method of systematic constraint handling and the illustrative example, a few conclusions can be drawn.
The results obtained by the method are readily applicable to commercial MPCs.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{textcomp}

\newcommand{\vect}[1] %vector notation
{{\bf {#1}}}
\newcommand{\npoly}{$n$-polytope}
\newcommand{\citepp}[4] %double parenthesis cite
{(\citealp[{#1}]{{#2}}; \citealp[{#3}]{{#4}})}
\newcommand{\bpm}{\begin{pmatrix}} %for matrix notation
\newcommand{\epm}{\end{pmatrix}}

@@

Mathematical rigour and unambiguous language for identifying constraint types were key design criteria. 
The application of the method is illustrated for a laboratory scale distillation column running commercial MPC packages.
\end{abstract}

@@

Table~\ref{tab:columnopcon} lists the operating conditions of the distillation column.
\begin{table}[htbp]
  \centering
  \begin{tabular}{llllll}
    \toprule
    \multicolumn{2}{c}{Variable} & \multicolumn{4}{c}{Constraints}\\
     && \multicolumn{2}{c}{Operating} & \multicolumn{2}{c}{Physical} \\
    \cmidrule(r){3-4} \cmidrule(r){5-6}
    && Low & High & Low & High \\ 
    \midrule
    Inputs &$R$ (mA)          & 11 & 15 & 4 & 20 \\
           &$T_{10~sp}$ (\textcelsius) & 78 & 82 & 25 & 90 \\[1.3ex]
    Outputs &$T_1$ (\textcelsius)     & 66 & 68 & 15 & 68 \\
            &$T_{8}$ (\textcelsius)   & 78 & 82 & 25 & 90 \\
    \bottomrule
  \end{tabular}
  \caption{Operating conditions of the laboratory distillation column.}
  \label{tab:columnopcon}
\end{table}

@@

Figure~\ref{fig:columnaisaos}(c) focuses on the intersection of the AOS and the DOS.
The calculated OI is 0.006 which confirms that only a very small operating region within the DOS is attainable.
It is also clear that the upper limit of 82~\textcelsius\ on $T_8$ is unrealistic as the maximum value of $T_8$ (in the desired operating region) is only 78.2~\textcelsius.

@@

The dark triangle in figure~\ref{fig:columnfitbox} represents the constraints defining the intersection.
An unmeasured variable needs to be added to the process model to implement the diagonal constraint ($0.88T_8-0.47T_1\leq 36.56$~\textcelsius).
Naming the new output $y_1$ and augmenting the process model matrix as shown in equation~\ref{eq:columnnewmodel} allows for the diagonal (linear) constraint to be expressed simply as {$y_1~\leq~36.56$~\textcelsius}.
\begin{equation}
  \label{eq:columnnewmodel}
  G_{new}= \bpm -0.0575 & 0.96 \\       % T1
                  -0.146  & 0.518 \\      % T8
                   0.0956 & 1.30 \\ \epm  %y1
\end{equation}

@@

\section{Conclusions}\label{sec:conclusions}
From the proposed method of systematic constraint handling and the illustrative example, a few conclusions can be drawn.
The results obtained by the method are readily applicable to commercial MPCs.
